Really Hard Instances for the Subgraph Isomorphism Problem

### 2015-11-15 paper/paper.tex
Tweaks

            \node [anchor=center, font=\Large] (A1) at (-1.5, -1.5) { $\hookleftarrow$ };
            \node [anchor=center, font=\Large] (A2) at ( 3.5, -1.5) { $\rightarrowtail$ };
        \end{scope}
    \end{tikzpicture}\\[0.5cm]
    \begin{tikzpicture}[scale=0.5]
        \begin{scope}
            \foreach \n in {1, ..., 6}{
                \node [draw, circle, fill=uofgcobalt, inner sep=1.5pt] (N1\n) at (\n, 0) {\n};
            }

@@

    \caption{On top, there is a non-induced isomorphism from the pattern graph, in the center, to the target
    on the right, mapping vertex 1 to 1, 2 to 3, 3 to 5 and 4 to 6. This is not an induced
    isomorphism, since there is an edge between 1 and 5 in the target but not between 1 and 3 in the
    pattern. The mapping from the pattern to the (same) target on the left, sending 1 to 2, 2 to 6, 3 to
    5 and 4 to 3, is both non-induced and induced.
    Below, the association graph encoding for the induced version. The bold clique of size
    four corresponds to the same mapping.}
    \label{figure:sip}
\end{figure}

@@

Throughout, our graphs are unlabelled, undirected, and do not have any loops (vertices which are
adjacent to themselves). We write $\operatorname{V}(G)$ for the vertex set of a graph $G$. A
\emph{non-induced subgraph isomorphism} from a graph $P$ (called the \emph{pattern}) to a graph $T$
(called the \emph{target}) is an injective mapping from $\operatorname{V}(P)$ to
$\operatorname{V}(T)$ which preserves adjacency---that is, for every adjacent $v$ and $w$ in
$\operatorname{V}(P)$, the vertices $i(v)$ and $i(w)$ are adjacent in $T$. An \emph{induced subgraph
isomorphism} additionally preserves non-adjacency---that is, if $v$ and $w$ are not adjacent in $P$,
then $i(v)$ and $i(w)$ must not be adjacent in $T$. We use the notation $i : P \rightarrowtail T$
for a non-induced isomorphism, and $i : P \hookrightarrow T$ for an induced isomorphism.

The \emph{order} of a graph is the cardinality of its vertex set.  We write $G(v, p)$ for a random
graph with $v$ vertices, and an edge between each distinct pair of vertices with independent
probability $p$.

The \emph{association graph encoding} of a subgraph isomorphism problem is constructed by creating a
new graph with a vertex for each pair $(p, t)$ of vertices from the pattern and target graphs
respectively. There is an edge between vertex $(p_1, t_1)$ and vertex $(p_2, t_2)$ if mapping $p_1$
to $t_1$ and $p_2$ to $t_2$ simultaneously is permitted. For the non-induced problem, permitted
means either $p_1$ is not adjacent to $p_2$, or both $p_1$ and $p_2$, and $t_1$ and $t_2$, are
adjacent; for the induced problem, it means that $p_1$ is adjacent to $p_2$ if and only if $t_1$ is
adjacent to $t_2$. Either way, it can be seen that a clique (a subset of vertices, each of which is
adjacent to every other in the subset) of size equal to the order of the pattern graph exists in the
association graph if and only if the problem is satisfiable (and the vertices selected correspond to
the assignments of the solution).

?? Cite max common subgraph.

>>>>

            \node [anchor=center, font=\Large] (A1) at (-1.5, -1.5) { $\hookleftarrow$ };
            \node [anchor=center, font=\Large] (A2) at ( 3.5, -1.5) { $\rightarrowtail$ };
        \end{scope}
    \end{tikzpicture}\\[0.75cm]
    \begin{tikzpicture}[scale=0.5]
        \begin{scope}
            \foreach \n in {1, ..., 6}{
                \node [draw, circle, fill=uofgcobalt, inner sep=1.5pt] (N1\n) at (\n, 0) {\n};
            }

@@

    \caption{On top, there is a non-induced isomorphism from the pattern graph, in the center, to the target
    on the right, mapping vertex 1 to 1, 2 to 3, 3 to 5 and 4 to 6. This is not an induced
    isomorphism, since there is an edge between 1 and 5 in the target but not between 1 and 3 in the
    pattern. The mapping from the pattern to the (same) target on the left, sending 1 to 2, 2 to 6, 3 to
    5 and 4 to 3, is both non-induced and induced.
    Below, the association graph encoding for the induced version: the highlighted clique
    corresponds to the same mapping.}
    \label{figure:sip}
\end{figure}

@@

Throughout, our graphs are unlabelled, undirected, and do not have any loops (vertices which are
adjacent to themselves).  The \emph{order} of a graph is the cardinality of its vertex set. We write
$\operatorname{V}(G)$ for the vertex set of a graph $G$.  We write $G(v, p)$ for a random graph with
$v$ vertices, and an edge between each distinct pair of vertices with independent probability $p$.

A \emph{non-induced subgraph isomorphism} from a graph $P$ (called the \emph{pattern}) to a graph
$T$ (called the \emph{target}) is an injective mapping from $\operatorname{V}(P)$ to
$\operatorname{V}(T)$ which preserves adjacency---that is, for every adjacent $v$ and $w$ in
$\operatorname{V}(P)$, the vertices $i(v)$ and $i(w)$ are adjacent in $T$. An \emph{induced subgraph
isomorphism} additionally preserves non-adjacency---that is, if $v$ and $w$ are not adjacent in $P$,
then $i(v)$ and $i(w)$ must not be adjacent in $T$. We use the notation $i : P \rightarrowtail T$
for a non-induced isomorphism, and $i : P \hookrightarrow T$ for an induced isomorphism.

The \emph{association graph encoding} of a subgraph isomorphism problem is constructed by creating a
new graph with a vertex for each pair $(p, t)$ of vertices from the pattern and target graphs
respectively. There is an edge between vertex $(p_1, t_1)$ and vertex $(p_2, t_2)$ if mapping $p_1$
to $t_1$ and $p_2$ to $t_2$ simultaneously is permitted. For the non-induced problem, permitted
means either $p_1$ is not adjacent to $p_2$, or both $p_1$ and $p_2$, and $t_1$ and $t_2$, are
adjacent; for the induced problem, it means that $p_1$ is adjacent to $p_2$ if and only if $t_1$ is
adjacent to $t_2$. Either way, it can be seen that a clique (a subset of vertices, each of which is
adjacent to every other in the subset) of size equal to the order of the pattern graph exists in the
association graph if and only if the problem is satisfiable, and the vertices selected correspond to
the assignments making the solution \citep{Levi:1973}.
